---
title: "linear model from Web"
author: "Louie A"
date: "Summer 2023"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```



### scatterplot


```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  labs(title = "SIMS and ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN
```







### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```
The numerical result is 0.6860073 between ARM ans SIMS. It is safe to to say that both variables correlate with strength 



### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The r- squared is 0.1406 and the residual standard error is 1.226. The more data you put into is, the more it will grow.


#### Predict at target point
```{r}
mydata <-data.frame(GRIP=88, ARM= 104)
predict.lm(model.1, mydata, interval ="prediction")
```
The Value that it predicted was 1.57 but, it can go to -0.863 to the upper interval.

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN

```
  
  
  
  
  
  
  
  

## Model 2 SIM~GRIP




### Now add in scatterplot
```{r}
basicNN <- ggplot(data, aes(y = SIMS, x = ARM)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ ARM") +
  theme(plot.title = element_text(hjust = 0.5))

basicNN

```

### Numerical results 
```{r}
cor(SIMS~GRIP,data=data)
```
The results for SIMS and GRIP is 0.6398458. SIMS and AMR have a higher correlation than SIMS and GRIP

### Inferential  (Build model.2)
  
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```
The residual error is 1.226 and th r - squared is 0.467. the residual error is better than SIMS and ARM




#### predict model.2 at target point


```{r}
predict.lm(model.1, mydata, interval ="prediction")
```
The  interval is going to be -0.08634158 and 4.022199


#### now add the model fit to our plot for model.2
  
```{r}
mygrip <- ggplot(data, aes(y = SIMS, x = GRIP)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "SIMS ~ GRIP") +
  theme(plot.title = element_text(hjust = 0.5))

mygrip

```





## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~GRIP,data=data)
```
The correlation is Larger than SIMS~AMR and SIMS ~GRIP. With all three the value is 0.6398458




### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

The model has a residual erorr of 1.144 and an r squared of 0.5422. this model is than SIMS~GRIP and SIMS~ARM. Model is SIMS = 0.37311 ARM + 0.24470 GRIP -5.433871


#### predict model.3 at target point

```{r}
predict.lm(model.3, mydata, interval ="prediction")
```
The interval goes from -1.71 to 2.9157

  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3

```{r}
anova(model.1, model.3)
```

```{r}
anova(model.2)
```

```{r}
anova(model.2)
```

```{r}
anova(model.3)
```


### Model.2 vs Model.3

## Informally compare Model.1 with model.2

